\subsection{Interface}
I'm open to adding more traits to the interface, assuming they are implementable
in a pure library solution.
\newline
Note, all implementations are denotated with \verb|...|, as they are
implementation specific. For a fill in, download the library referenced in
'Implementatation' sub-section.
\subsubsection{Arity}
Arity is the measure for the number of arguments a given function takes.
\begin{itemize}
\item[(1)] Return the arity (e.g. number of arguments) for a given callable type.
\item[(2)] Return whether the callable type has the queried number of arguments.
\end{itemize}
\begin{verbatim}
// (1)
template <typename Callable, typename... Args>
struct arity
    : std::integral_constant<size_t, ...>
{
};

// (2)
template <typename Callable, typename... Args>
struct is_nullary
    : std::integral_constant<bool, (arity<Callable, Args...>::value == 0)>
{
};
template <typename Callable, typename... Args>
struct is_unary
    : std::integral_constant<bool, (arity<Callable, Args...>::value == 1)>
{
};
template <typename Callable, typename... Args>
struct is_binary
    : std::integral_constant<bool, (arity<Callable, Args...>::value == 2)>
{
};
template <typename Callable, typename... Args>
struct is_ternary
    : std::integral_constant<bool, (arity<Callable, Args...>::value == 3)>
{
};
\end{verbatim}
Note; In the case of varying arguments (C-style ellipsis), \verb|std::arity| returns the
number of actual arguments.
\newline
Note; As default arguments are not a part of a function type (8.3.6), these will
always be 'ignored', in terms of \verb|std::arity|.
\newline
Note; For member functions, this will return the actual number of arguments, 
that is without the implicit object parameter, as this is handled seperately by
the traits; \verb|is_member_function|, and \verb|implicit_object_type|.

\subsubsection{Has Varying Arguments}
Return whether or not the callable type, accepts a varying number of arguments
(e.g. C style variadics, \verb|void func(...)|).
\begin{verbatim}
template <typename Callable, typename... Args>
struct has_varying_arguments
    : std::integral_constant<bool, ...>
{
};
\end{verbatim}
Note; Has nothing to do with variadic templates.

\subsubsection{Is const function}
Return whether the given member function, is declared const.
\begin{verbatim}
template <typename Callable, typename... Args>
struct is_const_function
    : std::integral_constant<bool, ...>
{
};
\end{verbatim}
Note; Only ever non-false for non-static member functions.

\subsubsection{Is function pointer}
Return whether the callable type is a function pointer.
\begin{verbatim}
template<typename Callable>
struct is_function_pointer
    : std::integral_constant<bool, ...>
{
};
\end{verbatim}

\subsubsection{Is member function}
Return whether the given callable type, is a member function.
\begin{verbatim}
template<typename Callable, typename... Args>
struct is_member_function
    : std::integral_constant<bool, ...>
{
};
\end{verbatim}
Note; This currently returns false for static functions, as we're not able to
disambiguate static functions from free functions.
The only way to disambiguate would be a compiler supported solution.

\subsubsection{Is static or free function}
Return whether the given callable type, is a static or free function.
\begin{verbatim}
template<typename Callable, typename... Args>
struct is_static_member_or_free_function
    : std::integral_constant<bool, ...>
{
};
\end{verbatim}
Note; See note in 'Is member function'. - Currently returns the complete
opposite of \verb|is_member_function|.

\subsubsection{Implicit object type}
Return the type of the implicit object parameter for a given member function.
\begin{verbatim}
template<typename Callable, typename... Args>
using implicit_object_type = ...;
\end{verbatim}
Note; This is only defined for callable's returning true for;
'Is member function'

\subsubsection{Parameter type}
Return the type of the i'th parameter for a given callable type.
\begin{verbatim}
template<int I, typename Callable, typename... Args>
using parameter_type = ...;
\end{verbatim}
Note; Is only defined for; $0 < I < \verb|std::arity<Callable>|$.
\newline
TODO; Figure if it's possible in a pure library solution, to retain qualifiers. 

\subsubsection{Return type}
Return the return type for a given callable type.
\begin{verbatim}
template<typename Callable, typename... Args>
using return_type = ...;
\end{verbatim}

\subsection{Usage}
The above traits can be used, in a few ways;
\subsubsection{Functions}
Using \verb|decltype(...)|, for declared functions;
\begin{verbatim}
void function(int, double);
std::return_type<decltype(function)> // void
std::parameter_type<0, decltype(function)> // int
\end{verbatim}
Using \verb|decltype(&...)|, for declared functions;
\begin{verbatim}
void function(int, double);
std::return_type<decltype(&function)> // void
std::parameter_type<0, decltype(&function)> // int
\end{verbatim}
Using template specifiction, for non-declared functions;
(which the above case, maps down to after decltype)
\begin{verbatim}
std::arity<void(...)>::value // 0
std::has_varying_arguments<void(...)>::value // true
\end{verbatim}

\subsubsection{Functors}
Passing functor types directly;
\begin{verbatim}
struct functor
{
    void operator()(int);
};
std::return_type<functor> // void
std::implicit_object_type<functor> // functor
\end{verbatim}
Passing functor types directly, but specifying the overload;
\begin{verbatim}
struct variadic_template_functor
{
    template <typename... Ts>
    void operator()(Ts..., ...);
};
std::arity<variadic_template_functor, int, double>::value // 2
std::has_varying_arguments<variadic_template_functor, int, double>::value // true
std::parameter_type<1, variadic_template_functor, int, double> // double
\end{verbatim}

\subsubsection{Member functions}
All class methods, are essencially function pointers, and hence will be called
the same way, just with a prefix;
\begin{verbatim}
struct klass
{
    void function(int);
    void const_function(int) const;
    static void static_function(int);
};
std::is_member_function<decltype(&klass::function)>::value // true
std::is_const_function<decltype(&klass::const_function)>::value // true
std::is_static_member_or_free_function<decltype(&klass::static_function)>::value // true
\end{verbatim}
Do note however, that for member functions (e.g. non-static functions defined on
the class), we need the '\verb|&|', while it can be left out for static functions;
\begin{verbatim}
std::is_static_member_or_free_function<decltype(klass::static_function)>::value // true
\end{verbatim}
The reason for why static functions are treated differently, is because these
are essentially free functions, and hence subject to the C rules for functions
and function pointers. 

Note; Templated and overloaded methods, are handled by explicitly specifying the
overload.

\subsubsection{Lambdas}
Lambdas are essentially functors, and hence behave as these, however as lambdas
are constructed as objects of an anonymous type, we'll need \verb|decltype(...)|
to get the underlaying type.
\begin{verbatim}
const auto lambda = [](int i){ return i; };
std::is_member_function<decltype(lambda)>::value // true
std::is_const_function<decltype(lambda)>::value // true
\end{verbatim}
Note; C++14 Polymorphic lambdas will be supported by means of explicitly specifying the
overload.

\subsubsection{Type overloading the call operator}
For all other types, which overload the call operator (\verb|operator()|), we have
behavior as in the functor case. For instance with std::function;
\begin{verbatim}
std::is_member_function<std::function<int(int)>>::value // true
std::is_same<std::return_type<std::function<int(int)>> // int
std::is_same<std::parameter_type<0, std::function<int(int)>> // int
\end{verbatim}

\subsection{Implementatation}
The proposal is concerned with the interface only, and hence compiler and
standard library vendors are free to do their implementation in any way they'd
like, be it compiler argumented or a pure library solution.

A pure library implementation has been developed, and is available at;
\begin{itemize}
\item \href{https://sourceforge.net/p/calltraits/code/ci/default/tree/code/combined/}
    {SourceForge Repository Link (may be updated since paper release)}
\item \href{http://sourceforge.net/code-snapshots/hg/c/ca/calltraits/code/calltraits-code-b1755248eaf854ea9cd0ef054cfb157de1b09daf.zip}
    {Download Code as Zip (always refers to the paper release)}
\end{itemize}
Note; This implementation currently makes use of a few C++1y features, however
the library can be implemented without these.
